How to Analyze Build Logs

### 2021-04-19 tse-paper/paper.tex
better motivation for study / metrics, use classification consistently

In this section, we present the results of the analysis phase along RQs 1.1 through
1.3.
\todo{if defining the RQs went up in the last section, rephrase the rqs here too}

@@

\Cref{fig:litsur:kind} depicts that there are two widely used ways to
extract information from build logs: either chunks (53\%) or
classifications (41\%).
Uses for chunks were extracting compilation errors,
test failures, or the duration of build
tasks~\citep{clemencic2014new,zhang2016android}.
Examples for
classifications were distinguishing failures caused by developers from
failures caused by infrastructure errors~\citep{lindqvist2019detection}
or determining whether projects use automated static analysis
tools~\citep{kavaler2019tool}.
Categorization is the more abstract representation, chunks
contain more information and could be turned into a categorization.

\Cref{fig:litsur:use} shows the aim for the
investigated works to analyze build logs, and the result also explains
the prevalence of classification in \Cref{fig:litsur:kind}.
The majority of works (46\%) used the outcome of their build log
analysis to drive further research---and it is science's aim to
classify and abstract.
Seo et al.~\citep{seo2014programmers}, for example,
categorized the types of compile errors encountered at
Google.
Other works (10\%) used the gained insights to give feedback to
developers.
For 8\% of the works was the retrieved information the input
to a next automatic onward processing step:
works chose
tests that should be part of a reduced, but still effective test
suite~\citep{shi2018evaluating} or filled     a data structure with
build information, an information source for further tools aiming
to fix a failing build~\citep{vassallo2018un-break}.

@@

{Parser} &
\citep{vassallo2018un-break} \citep{zhang2016android} \citep{seo2014programmers} \citep{hassan2019tackling} \citep{hassan2017automatic} \citep{chromy2007integration} \citep{mesbah2019deepdelta} \citep{wen2018blimp} \citep{kwon2018prioritizing} \citep{adams2007design} \citep{rahman2018impact} \citep{brandyberry2006continuous} \citep{tomassi2019bugswarm} \citep{ren2018automated} \citep{vassallo2019automated} \citep{cavalcanti2019impact} \citep{sippola2013qt} \citep{felipe2012towards} \citep{shi2018evaluating} \citep{urli2018design} \citep{selberg2012use}
 &
\includegraphics[width=0.35\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_21.pdf}
\\

{Regular expression} &
\citep{beller2017oops} \citep{hassan2017change} \citep{macho2018automatically} \citep{vassallo2017a-tale} \citep{lou2019history} \citep{hassan2017automatic} \citep{rott2019empirische} \citep{zampetti2019study} \citep{zhao2018comparing} \citep{rausch2017empirical} \citep{ghaleb2019studying} \citep{zampetti2017open} \citep{zhang2019large} \citep{kavaler2019tool} \citep{morris2010experience}
 &
\includegraphics[width=0.35\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_15.pdf}
\\

@@

% ----- information RQ 1.1 -----
In regards to the information that is targeted, \emph{most build log
analysis approaches aim to retrieve the reason a build failed} by
targeting ``errors'' or ``failing tests.''
% which is what we also do in LogChunks
\emph{The majority of approaches retrieves specific chunks of
text from the logs.} Chunks are the overarching concept to
the almost equally much used categorization: one can deduce a
categorization from chunks, but not vice versa.
\todo{catedorization was called classification before}

@@

In this section, we illustrate how the different chunk retrieval
techniques work practically on the example of the build logs
in \Cref{lst:logexamples}.
Marked in blue in \Cref{lst:logexamples}
are the chunks we target.
They contain the information on why the
corresponding build failed.
\Cref{lst:chunk-example} shows two excerpts
from Android build logs.
The chunk to be retrieved starts after a
colon and a line separator and before a capital letter.
It ends
before two line separators.
All these characteristics are consistent
with the two example chunks
from \Cref{lst:chunk-example}.
\Cref{lst:chunk-example-3} is very
different.
For example, it does not have the two extraneous newlines
after the chunk.

@@

If we train CTS with the example chunks from
\Cref{lst:chunk-example},
CTS will rank the lines from an analyzed build log which are most
similar to the chunks in the training examples.
It will then return the two lines ranked highest, as the chunks in
the training examples have on average 2.0 lines.
In this example,
CTS will have difficulty extracting the lines from
\Cref{lst:chunk-example-3} as there are no words that appear
in both the training and the test chunks.
The same applies if we train with the first chunk from
\Cref{lst:chunk-example} and try to retrieve the second chunk,
as the only shared word is ``task''.

Keywords that appear in or close to the chunk within
the build log configure the technique KWS\@.
For the examples from \Cref{lst:chunk-example} these could be
``FAILURE,'' ``wrong,'' or ``failed.''
The example from \Cref{lst:chunk-example-3} could be found
by searching for ``FAIL.''
If we train KWS with all three examples and the aforementioned
associated keywords, it would search for the three keywords from
\Cref{lst:chunk-example}, as they appear twice---most often within
the training set of three examples.

@@

For this article, we designed and implemented three automated chunk
retrieval techniques.
Our findings of techniques in the literature
mapping (~\Cref{sec:litsurresults} and \Cref{tab:litsur:techniques} in
particular) inspired the strategies that underlie them.
\Cref{tab:techniques} summarizes the techniques, which we describe here
in detail.

@@

\caro{To investigate which of the three techniques are feasible to
facilitate configurable build log analysis, we conduct an empirical
comparison on a large dataset of real world log files and excerpts.
}

In the literature mapping, we noted that previous work seemed to choose
a log analysis technique arbitrarily and that is a lack of guidance on
when to use which technique.
% add (see \Cref{sec:lit-sur:discussion}) ?
To address this, in this section, we conduct an empirical study
comparing the three novel chunk retrieval techniques we presented in
\Cref{sec:techniques}.

In particular, we are interested in how many examples a technique
should be trained with (\textbf{RQ2.1}),
how similar the structural representation of the targeted log chunks
has to be (\textbf{RQ2.2}), and how reliable the quality of the
produced retrievals is (\textbf{RQ2.3}).
This leads us to the following research questions:

@@

In the following, we first introduce the data set we created for this
study, and then describe the study design and its
results.
We answer these RQs separately for each technique.

@@

	We define a successful retrieval as one where all desired
	lines were extracted, therefore when recall is one.
	A retrieval is partially successful if at least some of the
	desired lines were extracted,
	and if the retrieved lines contain none of the desired lines
	a retrieval was unsuccessful.
\end{itemize}
\vspace{0.2cm}

@@

% absolute results? is there a nice word for these results
\Cref{fig:success-partial-all} compares the results all of chunk
retrievals techniques in our study.
It shows how many runs per technique were successful, partially
successful or unsuccessful in retrieving the chunk defined in the
test example.
CTS and KWS
extract at least some of the desired lines in 79\% and 88.5\%
of the chunk retrieval runs.
With 38.25\%, KWS also has the highest proportion of fully
successful extractions, followed by PBE with 34.5\%.
PBE has the
lowest number of partial retrievals with only 18 out of 400 chunk
retrieval runs.
All techniques clearly outperform the random baseline (RLR).

@@

Following from the results of the empirical study, in this section,
we give recommendations for
which types of log chunks and how many training examples
each technique is suited, as well as
how their output can be used further.
We summarize these recommendations in
\Cref{tab:single-technique-recommendations}.

@@

\textbf{Further Analysis of \emph{LogChunks}.}
We created the
\emph{LogChunks} data set \citep{brandt2020logchunks} specifically for
the comparative
study in this paper, though it can be the basis for various further
analyses of build log data.
For example, we can investigate the keywords to answer which
keywords developers use to mark errors that lead to a build failure
within build logs.

>>>>

In this section, we present the results of the analysis phase along RQs 1.1 through
1.3.

@@

\Cref{fig:litsur:kind} depicts that there are two widely used ways to
extract information from build logs: either chunks (53\%) or
classifications (41\%).
Uses for chunks were extracting compilation errors,
test failures, or the duration of build
tasks~\citep{clemencic2014new,zhang2016android}.
Examples for
classifications were distinguishing failures caused by developers from
failures caused by infrastructure errors~\citep{lindqvist2019detection}
or determining whether projects use automated static analysis
tools~\citep{kavaler2019tool}.
Classification is the more abstract representation, chunks
contain more information and could be turned into a classification.

\Cref{fig:litsur:use} shows the aim for the
investigated works to analyze build logs, and the result also explains
the prevalence of classification in \Cref{fig:litsur:kind}.
The majority of works (46\%) used the outcome of their build log
analysis to drive further research---and it is science's aim to
classify and abstract.
Seo et al.~\citep{seo2014programmers}, for example,
classified the types of compile errors encountered at
Google.
Other works (10\%) used the gained insights to give feedback to
developers.
For 8\% of the works was the retrieved information the input
to a next automatic onward processing step:
works chose
tests that should be part of a reduced, but still effective test
suite~\citep{shi2018evaluating} or filled     a data structure with
build information, an information source for further tools aiming
to fix a failing build~\citep{vassallo2018un-break}.

@@

{Parser} &
\citep{vassallo2018un-break,zhang2016android,seo2014programmers,hassan2019tackling,hassan2017automatic,chromy2007integration,mesbah2019deepdelta,wen2018blimp,kwon2018prioritizing,adams2007design,rahman2018impact,brandyberry2006continuous,tomassi2019bugswarm,ren2018automated,vassallo2019automated,cavalcanti2019impact,sippola2013qt,felipe2012towards,shi2018evaluating,urli2018design,selberg2012use}
 &
\includegraphics[width=0.35\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_21.pdf}
\\

{Regular expression} &
\citep{beller2017oops,hassan2017change,macho2018automatically,vassallo2017a-tale,lou2019history,hassan2017automatic,rott2019empirische,zampetti2019study,zhao2018comparing,rausch2017empirical,ghaleb2019studying,zampetti2017open,zhang2019large,kavaler2019tool,morris2010experience}
 &
\includegraphics[width=0.35\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_15.pdf}
\\

@@

% ----- information RQ 1.1 -----
In regards to the information that is targeted, \emph{most build log
analysis approaches aim to retrieve the reason a build failed} by
targeting ``errors'' or ``failing tests.''
% which is what we also do in LogChunks
\emph{The majority of approaches retrieves specific chunks of
text from the logs.} Chunks are the overarching concept to
the almost equally much used classification: one can deduce a
classification from chunks, but not vice versa.

@@

In this section, we illustrate how the different chunk retrieval
techniques work practically on the example of the build logs
in \Cref{lst:logexamples}.
Marked in blue in \Cref{lst:logexamples}
\todo{chunks not introduced yet}
are the chunks we target.
They contain the information on why the
corresponding build failed.
\Cref{lst:chunk-example} shows two excerpts
from Android build logs.
The chunk to be retrieved starts after a
colon and a line separator and before a capital letter.
It ends
before two line separators.
All these characteristics are consistent
with the two example chunks
from \Cref{lst:chunk-example}.
The chunk in \Cref{lst:chunk-example-3} is very
different.
For example, it does not have the two extraneous newlines
after the chunk.
\caro{introduce sturctural categories here?}

@@

If we train CTS with the example chunks from
\Cref{lst:chunk-example},
CTS will rank the lines from an analyzed build log whose vocabulary is
most similar to the chunks in the training examples.
It will then return the two lines ranked highest, as the chunks in
the training examples have on average 2.0 lines.
In this example,
CTS, trained on \Cref{lst:chunk-example},
will have difficulty extracting the lines from
\Cref{lst:chunk-example-3} as there are no words that appear
in both the training and the test chunks.
The same applies if we train with the first chunk from
\Cref{lst:chunk-example} and try to retrieve the second chunk,
as the only shared word is ``task''.

To configure KWS, the user has to provide search terms.
If log excerpts such as the ones from \Cref{lst:chunk-example}
are targeted, possible search terms would be
``FAILURE,'' ``wrong,'' or ``failed.''
The example from \Cref{lst:chunk-example-3} could be found
by searching for ``FAIL.''
If we train KWS with all three examples and the aforementioned
associated keywords, it would search for the three keywords from
\Cref{lst:chunk-example}, as they appear twice---most often within
the training set of three examples.

@@

For this article, we designed and implemented three automated chunk
retrieval techniques.
Our findings of techniques in the literature
mapping (\Cref{sec:litsurresults}) and \Cref{tab:litsur:techniques} in
particular) inspired the strategies that underlie them and our central
requirement of enabling a user to configure the technique to their use
case with little effort.
\Cref{tab:techniques} summarizes the techniques, which we describe here
in detail.

@@

% \caro{To investigate which of the three techniques are feasible to
% facilitate configurable build log analysis, we conduct an empirical
% comparison on a large dataset of real world log files and excerpts.
% }

% In the literature mapping, we noted that previous work seemed to choose
% a log analysis technique arbitrarily and that is a lack of guidance on
% when to use which technique.
% % add (see \Cref{sec:lit-sur:discussion}) ?
% To address this, in this section, we conduct an empirical study
% comparing the three novel chunk retrieval techniques we presented in
% \Cref{sec:techniques}.

We conduct an empirical study to compare how well the three
configurable chunk retrieval techniques can be applied to analyze
build logs.
With this evaluation we want to give a future user guidance on which
technique to choose for their build log analysis use case.

To understand the amount of configuration necessary, we investigate
how many log excerpts a technique
should be trained with (\textbf{RQ2.1}),
how similar the structural representation of the targeted log chunks
has to be (\textbf{RQ2.2}).
To determine whether the output of the build log analysis is suited
to be analyzed automatically or by a human user, without the need to
refer back to the full build log, we measure how
reliable the quality of the
produced retrievals is (\textbf{RQ2.3}).
This leads us to the following research questions:

@@

In the following, we introduce the data set we created for this
study, describe the study design and our results.
We discuss the answers to the RQs separately for each technique
and compare them to give recommendations on which technique
a future user should configure to analyze their build logs.

@@

	We define a successful retrieval as one where all desired
	lines were extracted, therefore when recall is one.
	A retrieval is partially successful if at least some of the
	desired lines were extracted,
  \todo{motivate this distinction: partially means not suited for
  automatic processing? unsuccessful for have to go back to log}
	and if the retrieved lines contain none of the desired lines
	a retrieval was unsuccessful.
\end{itemize}
\vspace{0.2cm}

@@

% absolute results? is there a nice word for these results
\Cref{fig:success-partial-all} compares the results all of chunk
retrievals techniques in our study.
It shows how many runs per technique were successful, partially
successful or unsuccessful in retrieving the complete
chunk defined in the test example.
CTS and KWS
extract at least some of the desired lines in 79\% and 88.5\%
of the chunk retrieval runs.
With 38.25\%, KWS also has the highest proportion of fully
successful extractions, followed by PBE with 34.5\%.
PBE has the
lowest number of partial retrievals with only 18 out of 400 chunk
retrieval runs.
All techniques clearly outperform the random baseline (RLR).

@@

Following from the results of the empirical study, in this section,
we discuss how accurate the three different techniques retrieve
information from build logs and infer how their
output can be used further.
Further, we give recommendations for
which types of log chunks and how many training examples
each technique is suited.
We summarize these recommendations in
\Cref{tab:single-technique-recommendations}.

@@

\textbf{Further Analysis of \emph{LogChunks}.}
We created the
\emph{LogChunks} data set~\citep{brandt2020logchunks} specifically for
the comparative
study in this paper, though it can be the basis for various further
analyses of build log data.
For example, we can investigate the keywords to answer which
keywords developers use to mark errors that lead to a build failure
within build logs.
